\chead{\color{benred8}\textsc{Ad Completorium \textemdash\ Compline}}
\thispagestyle{plain}

\begin{pages}
\begin{Leftside}
\firstlinenum{10000}\linenumincrement{10000}\beginnumbering\pstart

% COMPLETORIUM

\section*{Ad Completorium}
\label{sec:Compline}

\pend\pstart

\vspace{-4mm}

\begin{rubric}
Lector incipit :

\end{rubric}

\pend\pstart

\vspace{-2mm}

\gregorioscore[a]{LatinVersion/JubeDomine.gtex}

\pend\pstart

\redTitle{Benedictio.}

\pend\pstart

\vspace{1mm}

{\gresetinitiallines{0}
\gregorioscore[a]{LatinVersion/Completorium/NoctemQuietam.gtex}

}

\pend\pstart

\vspace{2mm}

\redTitle{Capitulum.\capitulumSpace \emph{1 Petri 5, 8--9.}}

\pend\pstart

\vspace{2mm}

\greannotation{}
\gregorioscore[a]{LatinVersion/CapitulumFratres.gtex}

\pend\pstart

\vspace{2mm}

{\gresetinitiallines{0}
\gregorioscore[a]{LatinVersion/AdjutoriumNostrum.gtex}

}

\pend\pstart

\vspace{2mm}

{\gresetinitiallines{0}
\gregorioscore[a]{LatinVersion/QuiFecitCaelum.gtex}

}

\pend\pstart

\vspace{2mm}

\begin{rubric}
\emph{\textcolor{black}{Pater no\libertineGlyph{s_t}er}} dicitur totum secreto. Deinde fit Confessio :

\end{rubric}

\pend\pstart

\begin{lettrinePar}
\lettrine{C}{o}nf\'{i}teor Deo omnipot\'{e}nti, be\'{a}t\ae\ Mar\'{i}\ae\ semper V\'{i}rgini, be\'{a}to Micha\'{e}li Arch\'{a}ngelo, be\'{a}to Jo\'{a}nni Bapt\'{i}\libertineGlyph{s_t}\ae , san\libertineGlyph{c_t}is Ap\'{o}\libertineGlyph{s_t}olis Petro et Paulo, et \'{o}mnibus San\libertineGlyph{c_t}is, quia pecc\'{a}vi nimis, cogitati\'{o}ne, verbo et \'{o}pere : \emph{\textcolor{benred8}{percutiendo sibi pectus}} mea culpa, mea culpa, mea m\'{a}xima culpa. Ideo precor be\'{a}tam Mar\'{i}am semper V\'{i}rginem, be\'{a}tum Micha\'{e}lem Arch\'{a}ngelum, be\'{a}tum Jo\'{a}nnem Bapt\'{i}\libertineGlyph{s_t}am, san\libertineGlyph{c_t}os Ap\'{o}\libertineGlyph{s_t}olos Petrum et Paulum, et omnes San\libertineGlyph{c_t}os, or\'{a}re pro me ad D\'{o}minum Deum no\libertineGlyph{s_t}rum.

\end{lettrinePar}

\pend\pstart

\begin{lettrinePar}
\lettrine{M}{i}sere\'{a}tur no\libertineGlyph{s_t}ri omn\'{i}potens Deus, et dim\'{i}ssis pecc\'{a}tis no\libertineGlyph{s_t}ris, perd\'{u}cat nos ad vitam \ae t\'{e}rnam. \Rbar\ Amen.

\end{lettrinePar}

\pend\pstart

\begin{lettrinePar}\lettrine{I}{n}dulg\'{e}ntiam, \grealtcross\ absoluti\'{o}nem, et remissi\'{o}nem peccat\'{o}rum no\libertineGlyph{s_t}r\'{o}rum tr\'{i}buat nobis omn\'{i}potens et mis\'{e}ricors D\'{o}minus. \Rbar\ Amen.

\end{lettrinePar}

\pend\pstart

\begin{rubric}
Deinde, clara voce, pollice signando sibi pe\libertineGlyph{c_t}us signo crucis, canitur :

\end{rubric}

\pend\pstart

{\gresetinitiallines{0}
\gregorioscore[a]{LatinVersion/ConverteNosDeus.gtex}

}

\pend\pstart

\begin{response}
\hspace{\sicutIncensumIndent}\Rbar\hspace{0.3mm} Et \hspace{7.5mm} av\'{e}rte \hspace{6.7mm} iram \hspace{5.5mm} tuam \hspace{0.3mm} a \hspace{1.0mm} nobis.

\end{response}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{LatinVersion/DeusInAdjutoriumFerial.gtex}

\pend\pstart

\begin{rubric}
A Septuagesima usque ad Pascha, loco \emph{\textcolor{black}{Allelúia}}, canitur :

\end{rubric}

\pend\pstart

\gregorioscore[a]{LatinVersion/LausTibi.gtex}

\pend\pstart

\vspace{5mm}

% COMPLETORIUM PSALMUS 4

\greannotation{{\upshape\Abar} VIII G}
\gregorioscore[a]{LatinVersion/Completorium/CompAnt-01.gtex}

\pend\pstart

\redTitle{Psalmus 4.}

\pend\pstart

\gregorioscore[a]{LatinVersion/Completorium/CompFL1.gtex}

\pend\pstart

\begin{psalmtext}
Miser\'{e}re \textbf{me}i, \GreStar\ et ex\'{a}udi orati\emph{\'{o}nem} \textbf{me}am.

F\'{i}lii h\'{o}minum \'{u}squequo gravi \textbf{cor}de? \GreStar\ ut quid dil\'{i}gitis vanit\'{a}tem et qu\'{\ae}ri\emph{tis men}\textbf{d\'{a}}cium?

Et scit\'{o}te qu\'{o}niam mirific\'{a}vit D\'{o}minus san\libertineGlyph{c_t}um \textbf{su}um, \GreStar\ D\'{o}minus ex\'{a}udiet me cum clam\'{a}ve\emph{ro ad} \textbf{e}um.

Irasc\'{i}mini, et nol\'{i}te pecc\'{a}re : \GreDagger\ qu\ae\ d\'{i}citis in c\'{o}rdibus \textbf{ves}tris, \GreStar\ in cub\'{i}libus ve\libertineGlyph{s_t}ris \emph{compun}\textbf{g\'{i}}mini.

Sacrific\'{a}te sacrif\'{i}cium ju\libertineGlyph{s_t}\'{i}ti\ae , \GreDagger\ et sper\'{a}te  in \textbf{D\'{o}}mino. \GreStar\ Multi dicunt : Quis o\libertineGlyph{s_t}\'{e}ndit \emph{nobis} \textbf{bo}na?

Sign\'{a}tum e\libertineGlyph{s_t} super nos lumen vultus tui \textbf{D\'{o}}mine : \GreStar\ ded\'{i}\libertineGlyph{s_t}i l\ae t\'{i}tiam in \emph{corde} \textbf{me}o.

A fru\libertineGlyph{c_t}u frum\'{e}nti, vini et \'{o}lei \textbf{su}i \GreStar\ mul\emph{tipli}\textbf{c\'{a}}ti sunt.

In pace in id\textbf{\'{i}p}sum \GreStar\ d\'{o}rmiam et \emph{requi}\textbf{\'{e}s}cam.

Qu\'{o}niam tu D\'{o}mine singul\'{a}riter \textbf{in} spe \GreStar\ con\emph{\libertineGlyph{s_t}itu}\textbf{\'{i}s}ti me.

Gl\'{o}ria Patri, et \textbf{F\'{i}}lio, \GreStar\ et Spir\'{i}\emph{tui} \textbf{Sanc}to.

Sicut erat in princ\'{i}pio, et nunc, et \textbf{sem}per, \GreStar\ et in s\'{\ae}cula s\ae cu\emph{l\'{o}rum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

% COMPLETORIUM PSALMUS 30

\redTitle{Psalmus 30.}

\pend\pstart

\gregorioscore[a]{LatinVersion/Completorium/CompFL2.gtex}

\pend\pstart

\begin{psalmtext}
Incl\'{i}na ad me aurem \textbf{tu}am, \GreStar\ acc\'{e}lera ut \emph{\'{e}ru}\textbf{as} me.

E\libertineGlyph{s_t}o mihi in Deum protect\'{o}rem : et in domum re\textbf{f\'{u}}gii, \GreStar\ ut sal\emph{vum me} \textbf{f\'{a}}cias.

Qu\'{o}niam fortit\'{u}do mea, et ref\'{u}gium meum \textbf{es} tu : \GreStar\ et propter nomen tuum ded\'{u}ces me, et e\emph{n\'{u}tri}\textbf{es} me.

Ed\'{u}ces me de l\'{a}queo hoc, quem abscond\'{e}runt \textbf{mi}hi : \GreStar\ qu\'{o}niam tu es pro\emph{t\'{e}\libertineGlyph{c_t}or} \textbf{me}us.

In manus tuas comm\'{e}ndo sp\'{i}ritum \textbf{me}um : \GreStar\ redem\'{i}\libertineGlyph{s_t}i me D\'{o}mine Deus \emph{veri}\textbf{t\'{a}}tis.

Gl\'{o}ria Patri, et \textbf{F\'{i}}lio, \GreStar\ et Spir\'{i}\emph{tui} \textbf{Sanc}to.

Sicut erat in princ\'{i}pio, et nunc, et \textbf{sem}per, \GreStar\ et in s\'{\ae}cula s\ae cu\emph{l\'{o}rum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

% COMPLELTORIUM PSALMUS 90

\redTitle{Psalmus 90.}

\pend\pstart

\gregorioscore[a]{LatinVersion/Completorium/CompFL3.gtex}

\pend\pstart

\begin{psalmtext}
Dicet D\'{o}mino : Susc\'{e}ptor meus es tu et ref\'{u}gium \textbf{me}um : \GreStar\ Deus meus sper\'{a}\emph{bo in} \textbf{e}um.

Qu\'{o}niam ipse liber\'{a}vit me de l\'{a}queo ve\textbf{n\'{a}n}tium, \GreStar\ et a \emph{verbo} \textbf{\'{a}s}pero.

Sc\'{a}pulis suis obumbr\'{a}bit \textbf{ti}bi : \GreStar\ et sub pennis e\emph{jus spe}\textbf{r\'{a}}bis.

Scuto circ\'{u}mdabit te v\'{e}ritas \textbf{e}jus : \GreStar\ non tim\'{e}bis a tim\'{o}\emph{re noc}\textbf{t\'{u}}rno.

A sag\'{i}tta vol\'{a}nte in die, \GreDagger\ a neg\'{o}tio perambul\'{a}nte in \textbf{t\'{e}}nebris : \GreStar\ ab inc\'{u}rsu, et d\ae m\'{o}nio me\emph{ridi}\textbf{\'{a}}no.

Cadent a l\'{a}tere tuo mille, \GreDagger\ et decem m\'{i}llia a dextris \textbf{tu}is : \GreStar\ ad te autem non ap\emph{propin}\textbf{qu\'{a}}bit.

Ver\'{u}mtamen \'{o}culis tuis conside\textbf{r\'{a}}bis : \GreStar\ et retributi\'{o}nem peccat\'{o}\emph{rum vi}\textbf{d\'{e}}bis.

Qu\'{o}niam tu es D\'{o}mine spes \textbf{me}a : \GreStar\ Alt\'{i}ssimum posu\'{i}\libertineGlyph{s_t}i ref\'{u}\emph{gium} \textbf{tu}um.

Non acc\'{e}det ad te \textbf{ma}lum : \GreStar\ et flag\'{e}llum non appropinqu\'{a}bit tabern\'{a}\emph{culo} \textbf{tu}o.

Qu\'{o}niam Angelis suis mand\'{a}vit \textbf{de} te : \GreStar\ ut cust\'{o}diant te in \'{o}mnibus \emph{viis} \textbf{tu}is.

In m\'{a}nibus por\textbf{t\'{a}}bunt te : \GreStar\ ne forte off\'{e}ndas ad l\'{a}pidem \emph{pedem} \textbf{tu}um.

Super \'{a}spidem et basil\'{i}scum ambu\textbf{l\'{a}}bis : \GreStar\ et conculc\'{a}bis le\'{o}nem \emph{et dra}\textbf{c\'{o}}nem.

Qu\'{o}niam in me sper\'{a}vit, liber\'{a}bo \textbf{e}um : \GreStar\ pr\'{o}tegam eum, qu\'{o}niam cogn\'{o}vit \emph{nomen} \textbf{me}um.

Clam\'{a}bit ad me, et ego ex\'{a}udiam eum : \GreDagger\ cum ipso sum in tribul\'{a}ti\textbf{o}ne : \GreStar\ er\'{i}piam eum et glorifi\emph{c\'{a}bo} \textbf{e}um.

Longit\'{u}dine di\'{e}rum repl\'{e}bo \textbf{e}um : \GreStar\ et o\libertineGlyph{s_t}\'{e}ndam illi salu\emph{t\'{a}re} \textbf{me}um.

Gl\'{o}ria Patri, et \textbf{F\'{i}}lio, \GreStar\ et Spir\'{i}\emph{tui} \textbf{Sanc}to.

Sicut erat in princ\'{i}pio, et nunc, et \textbf{sem}per, \GreStar\ et in s\'{\ae}cula s\ae cu\emph{l\'{o}rum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

% COMPLETORIUM PSALMUS 133

\redTitle{Psalmus 133.}

\pend\pstart

\gregorioscore[a]{LatinVersion/Completorium/CompFL4.gtex}

\pend\pstart

\begin{psalmtext}
Qui \libertineGlyph{s_t}atis in domo \textbf{D\'{o}}mini, \GreStar\ in \'{a}triis domus \emph{Dei} \textbf{nos}tri.

In n\'{o}\libertineGlyph{c_t}ibus ext\'{o}llite manus ve\libertineGlyph{s_t}ras in \textbf{sanc}ta, \GreStar\ et bened\'{i}\emph{cite} \textbf{D\'{o}}minum.

Bened\'{i}cat te D\'{o}minus ex \textbf{Si}on, \GreStar\ qui fecit c\ae\emph{lum et} \textbf{ter}ram.

Gl\'{o}ria Patri, et \textbf{F\'{i}}lio, \GreStar\ et Spir\'{i}\emph{tui} \textbf{Sanc}to.

Sicut erat in princ\'{i}pio, et nunc, et \textbf{sem}per, \GreStar\ et in s\'{\ae}cula s\ae cu\emph{l\'{o}rum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

\gregorioscore[a]{LatinVersion/Completorium/CompAnt-02.gtex}

\pend\pstart

% COMPLETORII HYMNUS

\subsection*{Hymnus.}

\pend\pstart

\begin{rubric}
Tonus Hymni \emph{\textcolor{black}{Te lucis ante t\'{e}rminum}} variatur secundum tempora aut fe\libertineGlyph{s_t}a :

\end{rubric}

\pend\pstart

\subsection*{Tonus in Feriis.}

\pend\pstart

\greannotation{VIII}
\gregorioscore[a]{LatinVersion/Completorium/TeLucisPAFeriis.gtex}

\pend\pstart

\subsection*{Tonus in Sabbatis et Dominicis.}

\pend\pstart

\greannotation{VIII}
\gregorioscore[a]{LatinVersion/Completorium/TeLucisPADominicis.gtex}

\pend\pstart

\subsection*{Tonus in Festis Simplicibus.}

\pend\pstart

\greannotation{VIII}
\gregorioscore[a]{LatinVersion/Completorium/TeLucisPASimplex.gtex}

\pend\pstart

\subsection*{Tonus in Festis Duplicibus.}

\pend\pstart

\greannotation{IV}
\gregorioscore[a]{LatinVersion/Completorium/TeLucisPADuplex.gtex}

\pend\pstart

\subsection*{Tonus in Tempore Adventus.}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{LatinVersion/Completorium/TeLucisAdvent.gtex}

\pend\pstart

\redTitle{Tonus in Tempore Quadragesim\ae.}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{LatinVersion/Completorium/TeLucisLent.gtex}

\pend\pstart

\subsection*{Tonus et doxologia in Fe\libertineGlyph{s_t}is B. M. Virginis aut Corporis Chri\libertineGlyph{s_t}i, ac infra eorum O\libertineGlyph{c_t}avas.}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{LatinVersion/Completorium/TeLucisBMVCorpChrist.gtex}

\pend\pstart

% COMPLETORIUM CAPITULUM

\subsection*{Capitulum.\capitulumSpace \emph{Jer. 14, 9.}}

\pend\pstart

\begin{rubric}
Tonus ut ad Vesperas ( p. \pageref{DominicaCapitulum} ).

\end{rubric}

\pend\pstart

\begin{response}\lettrine{T}{u} autem in nobis es D\'{o}mine, \GreDagger\ et nomen san\libertineGlyph{c_t}um tuum invoc\'{a}tum e\libertineGlyph{s_t} super nos : \GreStar\ ne derel\'{i}nquas nos D\'{o}mine Deus no\libertineGlyph{s_t}er. \Rbar\ Deo grátias.

\end{response}

\pend\pstart

% COMPLINE RESPONSORIUM BREVE

\redTitle{Responsorium Breve.}

\redTitle{Per Annum.}

\pend\pstart

\greannotation{VI}
\gregorioscore[a]{LatinVersion/Completorium/CompRespPA.gtex}

\pend\pstart

\gregorioscore[a]{LatinVersion/CustodiNosDomine.gtex}

\pend\pstart

\begin{response}
\hspace{1.0 mm}\Rbar\hspace{0.3mm} Sub \hspace{2.0mm} umbra \hspace{2.0mm} al\'{a}rum \hspace{2.0mm} tu\'{a}rum \hspace{1.2mm} pr\'{o}tege nos.

\end{response}

\pend\pstart

\subsection*{Tempore Adventus.}

\pend\pstart

\greannotation{IV}
\gregorioscore[a]{LatinVersion/Completorium/CompRespAdvent.gtex}

\pend\pstart

\gregorioscore[a]{LatinVersion/CustodiNosDomine.gtex}

\pend\pstart

\begin{response}
\hspace{1.0 mm}\Rbar\hspace{0.3mm} Sub \hspace{2.0mm} umbra \hspace{2.0mm} al\'{a}rum \hspace{2.0mm} tu\'{a}rum \hspace{1.2mm} pr\'{o}tege nos.

\end{response}

\pend\pstart

\subsection*{Tempore Quadrageism\ae.}

\pend\pstart

\greannotation{IV}
\gregorioscore[a]{LatinVersion/Completorium/CompRespLent.gtex}

\pend\pstart

\gregorioscore[a]{LatinVersion/CustodiNosDomine.gtex}

\pend\pstart

\begin{response}
\hspace{1.0 mm}\Rbar\hspace{0.3mm} Sub \hspace{2.0mm} umbra \hspace{2.0mm} al\'{a}rum \hspace{2.0mm} tu\'{a}rum \hspace{1.2mm} pr\'{o}tege nos.

\end{response}

\pend\endnumbering
\end{Leftside}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Rightside}

\firstlinenum{10000}\linenumincrement{10000}\beginnumbering\pstart

% COMPLINE

\section*{Compline}

\pend\pstart

\vspace{-4mm}

\begin{rubric}
The lector begins:

\end{rubric}

\pend\pstart

\vspace{-2mm}

\gregorioscore[a]{EnglishVersion/JubeDomine.gtex}

\pend\pstart

\redTitle{Blessing.}

\pend\pstart

\vspace{1mm}

\gregorioscore[a]{EnglishVersion/Completorium/NoctemQuietam.gtex}

\pend\pstart

\vspace{2mm}

\redTitle{Chapter.\capitulumSpace \emph{1 Peter 5, 8--9.}}

\pend\pstart

\vspace{2mm}

\greannotation{}
\gregorioscore[a]{EnglishVersion/CapitulumFratres.gtex}

\pend\pstart

\vspace{2mm}

{\gresetinitiallines{0}
\gregorioscore[a]{EnglishVersion/AdjutoriumNostrum.gtex}

}

\pend\pstart

\vspace{2mm}

{\gresetinitiallines{0}
\gregorioscore[a]{EnglishVersion/QuiFecitCaelum.gtex}

}

\pend\pstart

\vspace{2mm}

\begin{rubric}
An \emph{\textcolor{black}{Our Father}} is said, entirely secret. Then the Confession is made:

\end{rubric}

\pend\pstart

\begin{lettrinePar}\lettrine{I}{ c}onfess to almighty God, to blessed Mary ever Virgin, to blessed Michael the Archangel, to blessed John the Baptist, to the holy apostles Peter and Paul, and to all the saints, that I have sinned exceedingly in thought, word and deed, \emph{\textcolor{benred8}{striking the breast}} through my fault, through my fualt, through my most grievous fault. Therefore I beseech blessed Mary ever Virgin, blessed Michael the Archangel, blessed John the Baptist, the holy apostles Peter and Paul, and all the saints, to pray for me to the Lord our God.

\end{lettrinePar}

\pend\pstart

\begin{lettrinePar}\lettrine{M}{a}y almighty God have mercy upon us, forgive us our sins, and bring us to life everlasting. \Rbar\ Amen.

\end{lettrinePar}

\pend\pstart

\begin{lettrinePar}\lettrine{M}{a}y the almighty \grealtcross\ and merciful Lord grant us pardon, absolution, and remission of all our sins. \Rbar\ Amen.

\end{lettrinePar}

\pend\pstart

\begin{rubric}
Then, making the sign of the cross on one's breast with the thumb, the following is sung out loud:

\end{rubric}

\pend\pstart

{\gresetinitiallines{0}
\gregorioscore[a]{EnglishVersion/ConverteNosDeus.gtex}

}

\pend\pstart

\begin{response}
\hspace{\sicutIncensumIndent}\Rbar\hspace{0.3mm} And turn away \hspace{1.0mm}thine \hspace{0.5mm}anger \hspace{2.25mm} from us.

\end{response}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{EnglishVersion/DeusInAdjutoriumFerial.gtex}

\pend\pstart

\begin{rubric}
The following is sung from Septuagesima Sunday until Easter in place of \emph{\textcolor{black}{Alleluia}} :

\end{rubric}

\pend\pstart

\gregorioscore[a]{EnglishVersion/LausTibi.gtex}

\pend\pstart

\vspace{5mm}

% COMPLINE PSALM 4

\greannotation{{\upshape\Abar} VIII G}
\gregorioscore[a]{EnglishVersion/Completorium/CompAnt-01.gtex}

\pend\pstart

\redTitle{Psalm 4.}

\pend\pstart

\gregorioscore[a]{EnglishVersion/Completorium/CompFL1.gtex}

\pend\pstart

\begin{psalmtext}
%When I called upon him, the God of my justice \pipe\ heard me: \GreStar\ when I was in distress, thou \pipe\ hast enlarged me.

Have mercy \pipe\ on me: \GreStar\ and \pipe\ hear my \textbf{prayer}.

O ye sons of men, how long will you be dull \pipe\ of heart? \GreStar\ Why do you love vanity, and seek \pipe\ after lying?

Know ye also that the Lord hath made his holy one \pipe\ won\uline{derful}: \GreStar\ the Lord will hear me when I \pipe\ shall cry un\uline{to him}.

Be ye angry, and sin not: \GreDagger\ the things you say in \pipe\ your hearts, \GreStar\ be sorry for \pipe\ them upon \uline{your beds}.

Offer up the sacrifice of justice, \GreDagger\ and trust in \pipe\ the Lord: \GreStar\ many say, Who she- \pipe\ weth us good things?

The light of thy countenance, O Lord, is signed u- \pipe\ pon us: \GreStar\ thou hast given glad- \pipe\ \textbf{ness} in \uline{my heart}.

By the fruit of their corn, their wine, \pipe\ and oil, \GreStar\ \pipe\ they are mul\uline{tiplied}.

In peace in the \pipe\ selfsame \GreStar\ I will \pipe\ sleep, and I \uline{will rest}:

For thou, O Lord, singu- \pipe\ larly \GreStar\ hast settled \pipe\ me in \textbf{hope}.

Glory be to the Father, and to \pipe\ the Son, \GreStar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and ever \pipe\ shall be, \GreStar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

% COMPLINE PSALM 30

\redTitle{Psalm 30.}

\pend\pstart

\gregorioscore[a]{EnglishVersion/Completorium/CompFL2.gtex}

\pend\pstart

\begin{psalmtext}
%In thee, O Lord, have I hoped, let me never be con- \pipe\ founded: \GreStar\ deliver me \pipe\ in thy justice.

Bow down thy \pipe\ ear \uline{to me}: \GreStar\ make haste \pipe\ to deli\uline{ver me}.

Be thou unto me a God, a protector, and a house of \pipe\ refuge, \GreStar\ \pipe\ \textbf{to} save me.

For thou art my strength and my \pipe\ refuge; \GreStar\ and for thy name’s sake thou wilt lead \pipe\ me, and nourish me.

Thou wilt bring me out of this snare, which they have hidden \pipe\ for me: \GreStar\ for thou art \pipe\ my protector.

Into thy hands I commend my \pipe\ spirit: \GreStar\ thou hast redeemed me, O \pipe\ Lord, the God \uline{of truth}.

Glory be to the Father, and to \pipe\ the Son, \GreStar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and ever \pipe\ shall be, \GreStar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

% COMPLINE PSALM 90

\redTitle{Psalm 90.}

\pend\pstart

\gregorioscore[a]{EnglishVersion/Completorium/CompFL3.gtex}

\pend\pstart

\begin{psalmtext}
%He that dwelleth in the aid of the most High, \GreStar\ shall abide under the protection of the God of Jacob.

He shall say to the Lord: Thou art my protector, and my \pipe\ refuge: \GreStar\ my God, in \pipe\ \textbf{him} will \uline{I trust}.

For he hath delivered me from the snare of the \pipe\ hunters: \GreStar\ and \pipe\ from the sharp word.

He will overshadow thee with his \pipe\ shoulders: \GreStar\ and under his \pipe\ \textbf{wings} thou \uline{shalt trust}.

His truth shall compass thee with \pipe\ a shield: \GreStar\ thou shalt not be afraid of the terror \pipe\ of the \textbf{night}.

Of the arrow that flieth in the day, \GreDagger\ of the business that walketh about in \pipe\ the dark: \GreStar\ of invasion, or of the \pipe\ noonday devil.

A thousand shall fall at thy side, \GreDagger\ and ten thousand at \pipe\ thy \uline{right hand}: \GreStar\ but it shall \pipe\ not come nigh thee.

But thou shalt consider with \pipe\ thy eyes: \GreStar\ and shalt see the reward \pipe\ of the wicked.

Because thou, O Lord, art \pipe\ my hope: \GreStar\ thou hast made the most \pipe\ High thy refuge.

There shall no evil \pipe\ come to thee: \GreStar\ nor shall the scourge come \pipe\ near thy dwelling.

For he hath given his angels charge \pipe\ o\uline{ver thee}; \GreStar\ to keep thee in \pipe\ all thy \textbf{ways}.

In their hands they shall bear \pipe\ thee up: \GreStar\ lest thou dash thy \pipe\ foot against \uline{a stone}.

Thou shalt walk upon the asp and the \pipe\ ba\uline{silisk}: \GreStar\ and thou shalt trample under foot the lion \pipe\ and the dragon.

Because he hoped in me I will de- \pipe\ li\uline{ver him}: \GreStar\ I will protect him because he hath \pipe\ known my \textbf{name}.

He shall cry to me, and I will hear him: \GreDagger\ I am with him in tribu- \pipe\ lation, \GreStar\ I will deliver him, and I will \pipe\ glorify him.

I will fill him with length \pipe\ of days; \GreStar\ and I will shew him \pipe\ my salvation.

Glory be to the Father, and to \pipe\ the Son, \GreStar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and ever \pipe\ shall be, \GreStar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

% COMPLINE PSALM 133

\redTitle{Psalm 133.}

\pend\pstart

\gregorioscore[a]{EnglishVersion/Completorium/CompFL4.gtex}

\pend\pstart

\begin{psalmtext}
%Behold now bless ye the Lord, \GreStar\ all ye servants of the Lord:

Who stand in the house of \pipe\ the Lord, \GreStar\ in the courts of the house \pipe\ of our \textbf{God}.

In the nights lift up your hands to the ho- \pipe\ ly \uline{places}, \GreStar\ and bless \pipe\ ye the \textbf{Lord}.

May the Lord out of Si- \pipe\ on \uline{bless thee}, \GreStar\ he that made hea- \pipe\ ven and \textbf{earth}.

Glory be to the Father, and to \pipe\ the Son, \GreStar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and ever \pipe\ shall be, \GreStar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

\gregorioscore[a]{EnglishVersion/Completorium/CompAnt-02.gtex}

\pend\pstart

% COMPLINE HYMN

\subsection*{Hymn.}

\pend\pstart

\begin{rubric}
The tone for the Hymn \emph{\textcolor{black}{Te lucis ante t\'{e}rminum}} is varied according to the season and feast:

\end{rubric}

\pend\pstart

\subsection*{Weekday Tone.}

\pend\pstart

\greannotation{VIII}
\gregorioscore[a]{EnglishVersion/Completorium/TeLucisPAFeriis.gtex}

\pend\pstart

\subsection*{Saturday and Sunday Tone.}

\pend\pstart

\greannotation{VIII}
\gregorioscore[a]{EnglishVersion/Completorium/TeLucisPADominicis.gtex}

\pend\pstart

\subsection*{Tone for Simple Feasts.}

\pend\pstart

\greannotation{VIII}
\gregorioscore[a]{EnglishVersion/Completorium/TeLucisPASimplex.gtex}

\pend\pstart

\subsection*{Tone for Double Feasts.}

\pend\pstart

\greannotation{IV}
\gregorioscore[a]{EnglishVersion/Completorium/TeLucisPADuplex.gtex}

\pend\pstart

\subsection*{Tone in Advent.}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{EnglishVersion/Completorium/TeLucisAdvent.gtex}

\pend\pstart

\redTitle{Tone in Lent.}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{EnglishVersion/Completorium/TeLucisLent.gtex}

\pend\pstart

\subsection*{Tone and doxology for Feasts and Octaves of the Blessed Virgin Mary and Corpus Christi.}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{EnglishVersion/Completorium/TeLucisBMVCorpChrist.gtex}

\pend\pstart

% COMPLINE CHAPTER

\subsection*{Chapter.\capitulumSpace \emph{Jer. 14, 9.}}

\pend\pstart

\begin{rubric}
Sung as at Vespers (p. \pageref{DominicaCapitulum}).

\end{rubric}

\pend\pstart

\begin{response}\lettrine{T}{h}ou, O Lord, art among us, \GreDagger\ and thy Holy Name is called upon by us: \GreStar\ forsake us not, O Lord our God. \Rbar\ Thanks be to God.

\end{response}

\pend\pstart

% COMPLINE RESPONSORIUM BREVE

\redTitle{Short Responsory.}

\redTitle{Throughout the Year.}

\pend\pstart

\greannotation{VI}
\gregorioscore[a]{EnglishVersion/Completorium/CompRespPA.gtex}

\pend\pstart

\gregorioscore[a]{EnglishVersion/CustodiNosDomine.gtex}

\pend\pstart

\begin{response}
\hspace{1.0 mm}\Rbar\hspace{0.3mm} Protect \hspace{0.4mm} us \hspace{0.4mm} under \hspace{0.4mm} the \hspace{0.4mm} shadow of thy wings.

\end{response}

\pend\pstart

\subsection*{In Advent.}

\pend\pstart

\greannotation{IV}
\gregorioscore[a]{EnglishVersion/Completorium/CompRespAdvent.gtex}

\pend\pstart

\gregorioscore[a]{EnglishVersion/CustodiNosDomine.gtex}

\pend\pstart

\begin{response}
\hspace{1.0 mm}\Rbar\hspace{0.3mm} Protect \hspace{0.4mm} us \hspace{0.4mm} under \hspace{0.4mm} the \hspace{0.4mm} shadow of thy wings.

\end{response}

\pend\pstart

\subsection*{In Lent.}

\pend\pstart

\greannotation{IV}
\gregorioscore[a]{EnglishVersion/Completorium/CompRespLent.gtex}

\pend\pstart

\gregorioscore[a]{EnglishVersion/CustodiNosDomine.gtex}

\pend\pstart

\begin{response}
\hspace{1.0 mm}\Rbar\hspace{0.3mm} Protect \hspace{0.4mm} us \hspace{0.4mm} under \hspace{0.4mm} the \hspace{0.4mm} shadow of thy wings.

\end{response}

\pend\endnumbering
\end{Rightside}
\end{pages}
\Pages

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{pages}
\begin{Leftside}
\firstlinenum{10000}\linenumincrement{10000}\beginnumbering\pstart

% COMPLETORIUM NUNC DIMITTIS

\subsection*{Canticum Simeonis.\capitulumSpace \emph{Luc. 2, 29--32.}}

\pend\pstart

\greannotation{III a}
\gregorioscore[a]{LatinVersion/Completorium/CompNuncDimAnt-01.gtex}

\pend\pstart

\begin{psalmtext}
\emph{Quia} vid\'{e}runt \textbf{\'{o}}culi \textbf{me}i \GreStar\ salu\textbf{t\'{a}}re \textbf{tu}um :

\textbf{Quod} pa\textbf{r\'{a}}\libertineGlyph{s_t}i \GreStar\ ante f\'{a}ciem \'{o}mnium \textbf{po}pu\textbf{l\'{o}}rum :

\emph{Lumen} ad revelati\textbf{\'{o}}nem \textbf{g\'{e}nti}um, \GreStar\ et gl\'{o}riam plebis \textbf{tu}\ae\ \textbf{Is}rael.

\emph{Gl\'{o}ri}a \textbf{Pa}tri, et \textbf{F\'{i}li}o, \GreStar\ et Spi\textbf{r\'{i}}tui \textbf{Sanc}to.

\emph{Sicut} erat in princ\'{i}pio, et \textbf{nunc}, et \textbf{sem}per, \GreStar\ et in s\'{\ae}cula s\ae cu\textbf{l\'{o}}rum. \textbf{A}men.

\end{psalmtext}

\pend\pstart

\gregorioscore[a]{LatinVersion/Completorium/CompNuncDimAnt-02.gtex}

\pend\pstart

% COMPLETORIUM PRECES

\redTitle{Preces.}

\pend\pstart

\begin{rubric}
Sequentes Preces semper dicuntur, pr\ae terquam in Officio Duplici, et infra O\libertineGlyph{c_t}avas : quae in Feriali Officio tempore Adventus et Quadragesim\ae, et in Quatuor Temporibus, quando di\libertineGlyph{c_t}\ae\ sunt Preces in Vesperis, dicuntur flexis genibus.

\end{rubric}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{LatinVersion/Kyrie.gtex}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{LatinVersion/PaterNosterSecreto.gtex}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{LatinVersion/CredoSecreto.gtex}

\pend\pstart

\begin{response}
\Vbar\ Bened\'{i}\libertineGlyph{c_t}us es D\'{o}mine Deus patrum no\libertineGlyph{s_t}r\'{o}rum.
\Rbar\ Et laud\'{a}bilis et glori\'{o}sus in s\'{\ae}cula.

\Vbar\ Benedic\'{a}mus Patrem et F\'{i}lium cum San\libertineGlyph{c_t}o Sp\'{i}ritu.
\Rbar\ Laud\'{e}mus et superexalt\'{e}mus eum in s\'{\ae}cula.

\Vbar\ Bened\'{i}\libertineGlyph{c_t}us es D\'{o}mine in firmam\'{e}nto c\ae li.
\Rbar\ Et laud\'{a}bilis, et glori\'{o}sus, et superexalt\'{a}tus in s\'{\ae}cula.

\Vbar\ Bened\'{i}cat et cu\libertineGlyph{s_t}\'{o}diat nos omn\'{i}potens et mis\'{e}ricors D\'{o}minus.
\Rbar\ Amen.

\Vbar\ Dign\'{a}re D\'{o}mine no\libertineGlyph{c_t}e i\libertineGlyph{s_t}a.
\Rbar\ Sine pecc\'{a}to nos cu\libertineGlyph{s_t}od\'{i}re.

\Vbar\ Miser\'{e}re no\libertineGlyph{s_t}ri D\'{o}mine.
\Rbar\ Miser\'{e}re no\libertineGlyph{s_t}ri.

\Vbar\ Fiat miseric\'{o}rdia tua D\'{o}mine super nos. 
\Rbar\ Quem\'{a}dmodum sper\'{a}vimus in te.

\end{response}

\pend\pstart

{
\grechangedim{beforeinitialshift}{0.25mm}{scalable}
\grechangedim{afterinitialshift}{0.25mm}{scalable}
\greannotation{\upshape\Vbar}
\gregorioscore[a]{LatinVersion/DomineExaudi-short-03.gtex}

}

\pend\pstart

% COMPLETORIUM ORATIO

\begin{rubric}
Oratio canitur in Tono Simplici, ut in p.~\pageref{OratioSimplex}.

\end{rubric}

\pend\pstart

\subsection*{\textcolor{black}{Or\'{e}mus.}\capitulumSpace \emph{Oratio.}}

\pend\pstart

\begin{response}\lettrine{V}{i}sita, qu\'{\ae}sumus D\'{o}mine, habitati\'{o}nem i\libertineGlyph{s_t}am, et omnes ins\'{i}dias inim\'{i}ci ab ea longe rep\'{e}lle~:~\GreDagger\ Angeli tui san\libertineGlyph{c_t}i h\'{a}bitent in ea, qui nos in pace cu\libertineGlyph{s_t}\'{o}diant~; \GreStar\ et bened\'{i}\libertineGlyph{c_t}io tua sit super nos semper. Per D\'{o}minum no\libertineGlyph{s_t}rum Jesum Chri\libertineGlyph{s_t}um F\'{i}lium tuum : qui tecum vivit et regnat in unit\'{a}te Sp\'{i}ritus San\libertineGlyph{c_t}i Deus, per \'{o}mnia s\'{\ae}cula s\ae cul\'{o}rum. \Rbar\ Amen.

\end{response}

\pend\pstart

\begin{response}
\Vbar\ Dómine exáudi oratiónem meam. \Rbar\ Et clamor meus ad te véniat.

\end{response}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{LatinVersion/Completorium/CompBenedicamus.gtex}

\pend\pstart

\subsection*{Benedictio.}

\pend\pstart

\greannotation{}
\gregorioscore[a]{LatinVersion/BenedicatEtCustodiat.gtex}

\pend\pstart

\begin{rubric}
Et non dicitur \textcolor{black}{\emph{Fid\'{e}lium \'{a}nim\ae}}, sed immediate canitur una ex Antiphonis finalibus Beat\ae\ Mari\ae\ Virginis, cum Versu suo et Oratione, qu\ae\ in p.~\pageref{sec:AntBMV} notantur. Po\libertineGlyph{s_t}ea concluditur :

\end{rubric}

\pend\pstart

\begin{response}
\Vbar\ Div\'{i}num \grealtcross\ aux\'{i}lium m\'{a}neat semper nob\'{i}scum. \Rbar\ Amen.

\end{response}

\pend\pstart

\begin{rubric}
Deinde dicuntur secreto \textcolor{black}{\emph{Pater no\libertineGlyph{s_t}er}}, \textcolor{black}{\emph{Ave Mar\'{i}a}} et \textcolor{black}{\emph{Credo}}.

\end{rubric}

\pend\endnumbering
\end{Leftside}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Rightside}

\firstlinenum{10000}\linenumincrement{10000}\beginnumbering\pstart

% COMPLINE NUNC DIMITTIS

\subsection*{Canticle of Simeon.\capitulumSpace \emph{Luke. 2, 29--32.}}

\pend\pstart

\greannotation{III a}
\gregorioscore[a]{EnglishVersion/Completorium/CompNuncDimAnt-01.gtex}

\pend\pstart

\begin{psalmtext}
\emph{Because} my \pipe\ \textbf{eyes} have seen \GreStar\ \pipe\ thy salvation,

\pipe\ Which \uline{thou hast} prepared \GreStar\ before the \pipe\ face \uline{of all} peoples:

\emph{A light} to the reve- \pipe\ la\uline{tion of} the \uline{Gentiles}, \GreStar\ and the glory of thy \pipe\ people \uline{Isra}el.

\emph{Glory} be to the \pipe\ Fa\uline{ther, and to} the Son, \GreStar\ and to the \pipe\ Holy Spirit.

\emph{As it} was in the beginning, is now, and \pipe\ ever shall be, \GreStar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

\gregorioscore[a]{EnglishVersion/Completorium/CompNuncDimAnt-02.gtex}

\pend\pstart

% COMPLINE PRAYERS

\redTitle{Prayers.}

\pend\pstart

\begin{rubric}
The following Prayers are always said except on Double Feasts and during Octaves. During Advent, Lent and on Ember Days, when Prayers are also said at Vespers, they are said kneeling.

\end{rubric}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{EnglishVersion/Kyrie.gtex}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{EnglishVersion/PaterNosterSecreto.gtex}

\pend\pstart

\greannotation{\upshape\Vbar}
\gregorioscore[a]{EnglishVersion/CredoSecreto.gtex}

\pend\pstart

\begin{response}
\Vbar\ Blessed art thou, O Lord, God of our fathers.
\Rbar\ And worthy to be praised and glorious for ever.

\Vbar\ Let us bless the Father, and the Son, and the Holy Spirit.
\Rbar\ Let us praise and exalt him above all for ever.

\Vbar\ Blessed art thou, O Lord, in the firmament of heaven.
\Rbar\ And worthy to be praised and glorious and exalted above all for ever.

\Vbar\ May the almighty and merciful Lord bless and keep us.
\Rbar\ Amen.

\Vbar\ Vouchsafe, O Lord, this night.
\Rbar\ To keep us without sin.

\Vbar\ Have mercy upon us, O Lord.
\Rbar\ Have mercy upon us.

\Vbar\ Let thy mercy, O Lord, be upon us.
\Rbar\ As we have hoped in thee.

\end{response}

\pend\pstart

{
\grechangedim{beforeinitialshift}{0.25mm}{scalable}
\grechangedim{afterinitialshift}{0.25mm}{scalable}
\greannotation{\upshape\Vbar}
\gregorioscore[a]{EnglishVersion/DomineExaudi-short-03.gtex}

}

\pend\pstart

% COMPLINE ORATION

\begin{rubric}
The Oration is sung to the Simple Tone, as on p.~\pageref{OratioSimplex}.

\end{rubric}

\pend\pstart

\subsection*{\textcolor{black}{Let us pray.}\capitulumSpace \emph{Oration.}}

\pend\pstart

\begin{response}\lettrine{V}{i}sit, we beseech thee, O Lord, this dwelling, and drive far from it all snares of the enemy:~\GreDagger\ let thy Holy Angels dwell therein to keep us in peace,~\GreStar\ and may thy blessing be always upon us. Through our Lord Jesus Christ, thy Son, who liveth and reigneth with thee, in the unity of the Holy Spirit, God, for ever and ever. \Rbar\ Amen.

\end{response}

\pend\pstart

\begin{response}
\Vbar\ O Lord, hear my prayer. \Rbar\ And let my cry come unto thee.

\end{response}

\pend\pstart

\greannotation{II}
\gregorioscore[a]{EnglishVersion/Completorium/CompBenedicamus.gtex}

\pend\pstart

\subsection*{Blessing.}

\pend\pstart

\greannotation{}
\gregorioscore[a]{EnglishVersion/BenedicatEtCustodiat.gtex}

\pend\pstart

\begin{rubric}
The \textcolor{black}{\emph{May the souls of the faithful departed}} is not said, but one of the final Antiphons of the Blessed Virgin Mary is sung with its Verse and Oration. These are noted on p.~\pageref{sec:AntBMV}. Afterwards the Office is concluded thus:

\end{rubric}

\pend\pstart

\begin{response}
\Vbar\ May the divine \grealtcross\ assistance remain always with us. \Rbar\ Amen.

\end{response}

\pend\pstart

\begin{rubric}
Then the \textcolor{black}{\emph{Our Father}}, the \textcolor{black}{\emph{Hail Mary}} and the Creed are said secretly.

\end{rubric}

\pend\endnumbering
\end{Rightside}
\end{pages}
\Pages
