\begin{pages}
\begin{Leftside}
\firstlinenum{10000}\linenumincrement{10000}\beginnumbering\pstart

% FERIA SECUNDA AD VESPERAS

\section*{Feria Secunda ad Vesperas}

\pend\pstart

\begin{center}Pater no\libertineGlyph{s_t}er. Ave Mar\'{i}a.\end{center}

\pend\pstart

\chead{\color{benred8}\textsc{Feria II \textemdash\ Monday}}
\thispagestyle{plain}

\begin{response}\lettrine{D}{e}us \grealtcross\ in adjut\'{o}rium meum int\'{e}nde. \Rbar\ D\'{o}mine ad adjuv\'{a}ndum me fe\libertineGlyph{s_t}\'{i}na. Gl\'{o}ria Patri, et F\'{i}lio, et Spir\'{i}tui San\libertineGlyph{c_t}o. Sicut erat in princ\'{i}pio, et nunc, et semper, et in s\'{\ae}cula s\ae cul\'{o}rum. Amen. Allel\'{u}ia. \vel\ Laus tibi D\'{o}mine Rex \ae t\'{e}rn\ae\ gl\'{o}ri\ae .

\end{response}

\pend\pstart

% FERIA II 1 ANT

\setspaceafterinitial{7mm plus 0em minus 0em}
\setspacebeforeinitial{7mm plus 0em minus 0em}

\def\greinitialformat#1{%
{\fontsize{60}{60}\selectfont #1}%
}

\myaboveinitial{1 \Abar\ I g 2}
\includescore{LatinVersion/F2/F2Ant1-01.tex}

\pend\pstart

\def\greinitialformat#1{%
{\fontsize{43}{43}\selectfont #1}%
}

{
\centering
\textcolor{benred8}{Psalmus 114.}

}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2FL1.tex}
}

\pend\pstart

\begin{psalmtext}
Quia inclinávit aurem \textbf{su}am \textbf{mi}hi : \gresixstar\ et in diébus meis \emph{invo}\textbf{cá}bo.

Circumdedérunt me do\textbf{ló}res \textbf{mor}tis : \gresixstar\ et perícula inférni \emph{inve}\textbf{né}runt me.

Tribulatiónem et do\textbf{ló}rem in\textbf{vé}ni : \gresixstar\ et nomen Dómini \emph{invo}\textbf{cá}vi.

O Dómine líbera ánimam meam : \gredagger\ miséricors Dómi\textbf{nus}, et \textbf{jus}tus, \gresixstar\ et Deus no\libertineGlyph{s_t}er \emph{mise}\textbf{ré}tur.

Cu\libertineGlyph{s_t}ódiens \textbf{pár}vulos \textbf{Dó}minus : \gresixstar\ humiliátus sum, et \emph{libe}\textbf{rá}vit me.

Convértere ánima mea in \textbf{ré}quiem \textbf{tu}am : \gresixstar\ quia Dóminus bene\emph{fécit} \textbf{ti}bi.

Quia erípuit ánimam meam de morte : \gredagger\ óculos \textbf{me}os a \textbf{lác}rimis, \gresixstar\ pedes me\emph{os a} \textbf{lap}su.

Pla\textbf{cé}bo \textbf{Dó}mino \gresixstar\ in regió\emph{ne vi}\textbf{vó}rum.

Glória \textbf{Pat}ri, et \textbf{Fí}lio, \gresixstar\ et Spirí\emph{tui} \textbf{Sanc}to.

Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per, \gresixstar\ et in sǽcula sæcu\emph{lórum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2Ant1-02.tex}

}

\pend\pstart

% FERIA II 2 ANT

\setspaceafterinitial{6.5mm plus 0em minus 0em}
\setspacebeforeinitial{6.5mm plus 0em minus 0em}

\myaboveinitial{2 \Abar\ VIII a}
\includescore{LatinVersion/F2/F2FL2.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalmus 115.}

}

\pend\pstart

\begin{psalmtext}
Ego dixi in excéssu \textbf{me}o : \gresixstar\ Omnis \emph{homo} \textbf{men}dax.

Quid retríbuam \textbf{Dó}mino, \gresixstar\ pro ómnibus quæ retrí\emph{buit} \textbf{mi}hi?

Cálicem salutáris ac\textbf{cí}piam : \gresixstar\ et nomen Dómini \emph{invo}\textbf{cá}bo.

Vota mea Dómino reddam coram omni pópulo \textbf{e}jus : \gresixstar\ pretiósa in conspé\libertineGlyph{c_t}u Dómini mors sanc\emph{tórum} \textbf{e}jus :

O Dómine quia ego servus \textbf{tu}us : \gresixstar\ ego servus tuus, et fílius an\emph{cíllæ} \textbf{tu}æ.

Dirupí\libertineGlyph{s_t}i víncula mea : \gredagger\ tibi sacrificábo hó\libertineGlyph{s_t}iam \textbf{lau}dis, \gresixstar\ et nomen Dómini \emph{invo}\textbf{cá}bo.

Vota mea Dómino reddam in conspé\libertineGlyph{c_t}u omnis pópuli \textbf{e}jus, \gresixstar\ in átriis domus Dómini, in médio tu\emph{i Je}\textbf{rú}salem.

Glória Patri, et \textbf{Fí}lio, \gresixstar\ et Spirí\emph{tui} \textbf{Sanc}to.

Sicut erat in princípio, et nunc, et \textbf{sem}per, \gresixstar\ et in sǽcula sæcu\emph{lórum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2Ant2-02.tex}

}

\pend\pstart

% FERIA II 3 ANT

\setspaceafterinitial{6mm plus 0em minus 0em}
\setspacebeforeinitial{6mm plus 0em minus 0em}

\myaboveinitial{3 \Abar\ VI F}
\includescore{LatinVersion/F2/F2FL3.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalmus 116.}

}

\pend\pstart

\begin{psalmtext}
Quóniam confirmáta e\libertineGlyph{s_t} super nos misericórdi\emph{a} \textbf{e}jus : \gresixstar\ et véritas Dómini manet \emph{in æ}\textbf{tér}num.

Glória Patri, \emph{et} \textbf{Fí}lio, \gresixstar\ et Spirí\emph{tui} \textbf{Sanc}to.

Sicut erat in princípio, et nunc, \emph{et} \textbf{sem}per, \gresixstar\ et in sǽcula sæcu\emph{lórum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2Ant3-02.tex}

}

\pend\pstart

% FERIA II 4 ANT

\setspaceafterinitial{2.5mm plus 0em minus 0em}
\setspacebeforeinitial{2.5mm plus 0em minus 0em}

\myaboveinitial{4 \Abar\ E}
\includescore{LatinVersion/F2/F2Ant4-01.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalmus 119.}

}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2FL4.tex}
}

\pend\pstart

\begin{psalmtext}
Dómine líbera ánimam meam a lábiis i\textbf{ní}quis, \gresixstar\ et a \textbf{lin}gua do\textbf{ló}sa.

Quid detur tibi, aut quid apponátur \textbf{ti}bi \gresixstar\ ad \textbf{lin}guam do\textbf{ló}sam?

Sagíttæ poténtis a\textbf{cú}tæ, \gresixstar\ cum carbónibus de\textbf{so}la\textbf{tó}riis.

Heu mihi, quia incolátus meus prolongátus e\libertineGlyph{s_t} : \gredagger\ habitávi cum habitántibus \textbf{Ce}dar : \gresixstar\ multum íncola fuit \textbf{á}nima \textbf{me}a.

Cum his qui odérunt pacem, eram pa\textbf{cí}ficus : \gresixstar\ cum loquébar illis, impu\textbf{gná}bant me \textbf{gra}tis.

Glória Patri, et \textbf{Fí}lio, \gresixstar\ et Spi\textbf{rí}tui \textbf{Sanc}to.

Sicut erat in princípio, et nunc, et \textbf{sem}per, \gresixstar\ et in sǽcula sæcu\textbf{ló}rum. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2Ant4-02.tex}

}

\pend\pstart

% FERIA II 5 ANT

\setspaceafterinitial{4.5mm plus 0em minus 0em}
\setspacebeforeinitial{4.5mm plus 0em minus 0em}

\myaboveinitial{5 \Abar\ I D}
\includescore{LatinVersion/F2/F2Ant5-01.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalmus 120.}

}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2FL5.tex}
}

\pend\pstart

\begin{psalmtext}
Auxílium \textbf{me}um a \textbf{Dó}mino, \gresixstar\ qui fecit cæ\emph{lum et} \textbf{ter}ram.

Non det in commotiónem \textbf{pe}dem \textbf{tu}um : \gresixstar\ neque dormítet \emph{qui cus}\textbf{tó}dit te.

Ecce non dormitábit \textbf{ne}que \textbf{dór}miet, \gresixstar\ qui cus\emph{tódit} \textbf{Is}rael.

Dóminus cu\libertineGlyph{s_t}ódit te, Dóminus pro\textbf{téc}tio \textbf{tu}a, \gresixstar\ super manum déx\emph{teram} \textbf{tu}am.

Per diem \textbf{sol} non \textbf{u}ret te : \gresixstar\ neque lu\emph{na per} \textbf{noc}tem.

Dóminus cu\libertineGlyph{s_t}ódit te ab \textbf{om}ni \textbf{ma}lo : \gresixstar\ cu\libertineGlyph{s_t}ódiat ánimam \emph{tuam} \textbf{Dó}minus.

Dóminus cu\libertineGlyph{s_t}ódiat intróitum tuum et \textbf{éx}itum \textbf{tu}um : \gresixstar\ ex hoc nunc, et us\emph{que in} \textbf{sǽ}culum.

Glória \textbf{Pa}tri, et \textbf{Fí}lio, \gresixstar\ et Spirí\emph{tui} \textbf{Sanc}to.

Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per, \gresixstar\ et in sǽcula sæcu\emph{lórum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2Ant5-02.tex}

}

\pend\pstart

% FERIA II CAPITULUM

\subsection*{Capitulum.\capitulumSpace \emph{2 Cor. 1, 3--4.}}

\pend\pstart

\begin{response}\lettrine{B}{e}nedí\libertineGlyph{c_t}us Deus, et Pater Dómini no\libertineGlyph{s_t}ri Jesu Chri\libertineGlyph{s_t}i, \gredagger\ Pater misericordiárum, et Deus totíus consolatiónis, \gresixstar\ qui consolátur nos in omni tribulatióne no\libertineGlyph{s_t}ra. \Rbar\ Deo grátias.

\end{response}

\pend\pstart

% FERIA II HYMNUS HIEME

\subsection*{Hymnus.\\Tonus in Hieme.}

\pend\pstart

\setspaceafterinitial{3mm plus 0em minus 0em}
\setspacebeforeinitial{3.8mm plus 0em minus 0em}

\myaboveinitial{VIII}
\includescore{LatinVersion/F2/F2Hym-Hieme.tex}

\pend\pstart

\begin{response}
\Vbar\ Dirig\'{a}tur D\'{o}mine or\'{a}tio mea.\\
\Rbar\ Sicut inc\'{e}nsum in consp\'{e}\libertineGlyph{c_t}u tuo.

\end{response}

\pend\pstart

% FERIA II HYMNUS AESTATE

\subsection*{Tonus in \AE \libertineGlyph{s_t}ate.}

\pend\pstart

\setspaceafterinitial{2.2mm plus 0em minus 0em}
\setspacebeforeinitial{3.2mm plus 0em minus 0em}

\myaboveinitial{I}
\includescore{LatinVersion/F2/F2Hym-Aestate.tex}

\pend\pstart

\begin{response}
\Vbar\ Dirig\'{a}tur D\'{o}mine or\'{a}tio mea.\\
\Rbar\ Sicut inc\'{e}nsum in consp\'{e}\libertineGlyph{c_t}u tuo.

\end{response}

\pend\pstart

% FERIA II MAGNIFICAT

\subsection*{Canticum Beat\ae\ Mari\ae\ Virginis.\capitulumSpace \emph{Luc. 1, 46--55.}}

\pend\pstart

\setspaceafterinitial{3mm plus 0em minus 0em}
\setspacebeforeinitial{3.8mm plus 0em minus 0em}

\myaboveinitial{VIII G}
\includescore{LatinVersion/F2/F2MagAnt-01.tex}

\pend\pstart

\begin{psalmtext}
Quia resp\'{e}xit humilit\'{a}tem anc\'{i}ll\ae\ \textbf{su}\ae\ : \gresixstar\ ecce enim ex hoc be\'{a}tam me dicent omnes gene\emph{rati}\textbf{\'{o}}nes.

Quia fecit mihi magna qui \textbf{po}tens e\libertineGlyph{s_t} : \gresixstar\ et san\libertineGlyph{c_t}um \emph{nomen} \textbf{e}jus.

Et miseric\'{o}rdia ejus a prog\'{e}nie in pro\textbf{g\'{e}}nies \gresixstar\ tim\'{e}n\emph{tibus} \textbf{e}um.

Fecit pot\'{e}ntiam in br\'{a}chio \textbf{su}o : \gresixstar\ disp\'{e}rsit sup\'{e}rbos mente \emph{cordis} \textbf{su}i.

Dep\'{o}suit pot\'{e}ntes de \textbf{se}de, \gresixstar\ et exal\emph{t\'{a}vit} \textbf{h\'{u}}miles.

Esuri\'{e}ntes impl\'{e}vit \textbf{bo}nis : \gresixstar\ et d\'{i}vites dim\'{i}\emph{sit i}\textbf{n\'{a}}nes.

Susc\'{e}pit Israel p\'{u}erum \textbf{su}um, \gresixstar\ record\'{a}tus miseric\'{o}r\emph{di\ae} \textbf{su}\ae.

Sicut loc\'{u}tus e\libertineGlyph{s_t} ad patres \textbf{nos}tros, \gresixstar\ Abraham, et s\'{e}mini e\emph{jus in} \textbf{s\'{\ae}}cula.

Glória Patri, et \textbf{Fí}lio, \gresixstar\ et Spirí\emph{tui} \textbf{Sanc}to.

Sicut erat in princípio, et nunc, et \textbf{sem}per, \gresixstar\ et in sǽcula sæcu\emph{lórum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{LatinVersion/F2/F2MagAnt-02.tex}

}

\pend\endnumbering
\end{Leftside}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{Rightside}

\firstlinenum{10000}\linenumincrement{10000}\beginnumbering\pstart

% MONDAY AT VESPERS

\section*{Monday at Vespers}

\pend\pstart

\begin{center}Our Father. Hail Mary.\end{center}

\pend\pstart

\begin{response}\lettrine{O}{} God, \grealtcross\ come to mine assistance. \Rbar\ O Lord, make haste to help me. Glory be to the Father, and to the Son, and to the Holy Spirit. As it was in the beginning, is now, and ever shall be, world without end. Amen. Alleluia. \veleng\~Praise be to thee, O Lord, Kind of eternal glory.

\end{response}

\pend\pstart

% MONDAY 1 ANT

\setspaceafterinitial{0mm plus 0em minus 0em}
\setspacebeforeinitial{0mm plus 0em minus 0em}

\def\greinitialformat#1{%
{\fontsize{60}{60}\selectfont #1}%
}

\myaboveinitial{1 \Abar\ I g 2}
\includescore{EnglishVersion/F2/F2Ant1-01.tex}

\pend\pstart

\def\greinitialformat#1{%
{\fontsize{43}{43}\selectfont #1}%
}

{
\centering
\textcolor{benred8}{Psalm 114.}

}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2FL1.tex}
}

\pend\pstart

\begin{psalmtext}
%I have loved, because the Lord will hear \gresixstar\ the voice of my prayer.

Because he hath inclined his \pipe\ ear unto me: \gresixstar\ and in my days I will \pipe\ call upon him.

The sorrows of \pipe\ death have com\uline{passed me}: \gresixstar\ and the perils of hell \pipe\ have \textbf{found} me.

I met with \pipe\ trou\uline{ble and} sorrow: \gresixstar\ and I called upon the \pipe\ \textbf{name} \uline{of the} Lord.

O Lord, deliver my soul. \gredagger\ The Lord is \pipe\ mer\uline{ciful} and just, \gresixstar\ and our God \pipe\ sheweth mercy.

The Lord is the \pipe\ kee\uline{per of} lit\uline{tle ones}: \gresixstar\ I was humbled, and \pipe\ he de\uline{livered} me.

Turn, O my \pipe\ soul, \uline{into} thy rest: \gresixstar\ for the Lord hath been boun- \pipe\ tiful to thee.

For he hath delivered my soul from death: \gredagger\ my \pipe\ \textbf{eyes} from tears, \gresixstar\ my \pipe\ feet from falling.

I will \pipe\ please the \textbf{Lord} \gresixstar\ in the land \pipe\ of the living.

Glory be to the \pipe\ Fa\uline{ther, and} to \uline{the Son}, \gresixstar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and \pipe\ ever shall be, \gresixstar\ world without \pipe\ end. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2Ant1-02.tex}

}

\pend\pstart

% MONDAY 2 ANT

\setspaceafterinitial{6mm plus 0em minus 0em}
\setspacebeforeinitial{6mm plus 0em minus 0em}

\myaboveinitial{2 \Abar\ VIII a}
\includescore{EnglishVersion/F2/F2FL2.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalm 115.}

}

\pend\pstart

\begin{psalmtext}
%I have believed, therefore have I spoken; \gresixstar\ but I have been humbled exceedingly.

I said in my \pipe\ excess: \gresixstar\ Every man \pipe\ is a liar.

What shall I render to \pipe\ the Lord, \gresixstar\ for all the things that he hath \pipe\ rendered to me?

I will take the chalice of \pipe\ sal\uline{vation}; \gresixstar\ and I will call upon the name \pipe\ of the \textbf{Lord}.

I will pay my vows to the Lord before all \pipe\ his \uline{people}: \gresixstar\ precious in the sight of the Lord is the death \pipe\ of his \textbf{saints}.

O Lord, for I am \pipe\ thy \uline{servant}: \gresixstar\ I am thy servant, and the son \pipe\ of thy handmaid.

Thou hast broken my bonds: \gredagger\ I will sacrifice to thee the sacrifice \pipe\ of praise, \gresixstar\ and I will call upon the name \pipe\ of the \textbf{Lord}.

I will pay my vows to the Lord in the sight of all \pipe\ his \uline{people}: \gresixstar\ in the courts of the house of the Lord, in the midst of thee, \pipe\ O Jeru\uline{salem}.

Glory be to the Father, and to \pipe\ the Son, \gresixstar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and ever \pipe\ shall be, \gresixstar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2Ant2-02.tex}

}

\pend\pstart

% MONDAY 3 ANT

\setspaceafterinitial{6mm plus 0em minus 0em}
\setspacebeforeinitial{6mm plus 0em minus 0em}

\myaboveinitial{3 \Abar\ VI F}
\includescore{EnglishVersion/F2/F2FL3.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalm 116.}

}

\pend\pstart

\begin{psalmtext}
%Praise the Lord, all ye nations: * praise him, all ye people.

For his mercy is confirmed \pipe\ upon us: \gresixstar\ and the truth of the Lord remain- \pipe\ eth for ever.

Glory be to the Father, and \pipe\ to the Son, \gresixstar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and ev- \pipe\ er shall be, \gresixstar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2Ant3-02.tex}

}

\pend\pstart

% MONDAY 4 ANT

\setspaceafterinitial{2.5mm plus 0em minus 0em}
\setspacebeforeinitial{2.5mm plus 0em minus 0em}

\myaboveinitial{4 \Abar\ E}
\includescore{EnglishVersion/F2/F2Ant4-01.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalm 119.}

}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2FL4.tex}
}

\pend\pstart

\begin{psalmtext}
%In my trouble I cried to the Lord: \gresixstar\ and he heard me.

O Lord, deliver my soul from \pipe\ wick\uline{ed lips}, \gresixstar\ and \pipe\ a \uline{deceit}ful tongue.

What shall be given to thee, or what shall be added \pipe\ to thee, \gresixstar\ to \pipe\ a \uline{deceit}ful tongue?

The sharp arrows of the \pipe\ mighty, \gresixstar\ with \pipe\ coals that lay waste.

Woe is me, that my sojourning is prolonged! \gredagger\ I have dwelt with the inhabitants of \pipe\ Cedar: \gresixstar\ my soul hath been \pipe\ long a so\uline{journer}.

With them that hated peace I was \pipe\ pea\uline{ceable}: \gresixstar\ when I spoke to them they fought a- \pipe\ gainst \uline{me with}out cause.

Glory be to the Father, and \pipe\ to \uline{the Son}, \gresixstar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and ever \pipe\ shall be, \gresixstar\ world with- \pipe\ out end. Amen.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2Ant4-02.tex}

}

\pend\pstart

% MONDAY 5 ANT

\setspaceafterinitial{2.5mm plus 0em minus 0em}
\setspacebeforeinitial{2.5mm plus 0em minus 0em}

\myaboveinitial{5 \Abar\ I D}
\includescore{EnglishVersion/F2/F2Ant5-01.tex}

\pend\pstart

{
\centering
\textcolor{benred8}{Psalm 120.}

}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2FL5.tex}
}

\pend\pstart

\begin{psalmtext}
%I have lifted up my eyes to the mountains, \gresixstar\ from whence help shall come to me.

My help is \pipe\ from the \textbf{Lord}, \gresixstar\ who made \pipe\ heaven and earth.

May he not suffer thy \pipe\ foot to be moved: \gresixstar\ neither let him slum- \pipe\ ber that \uline{keepeth} thee.

Behold he shall neither \pipe\ slumber nor sleep, \gresixstar\ that \pipe\ keepeth \uline{Isra}el.

The Lord is thy keeper, the Lord is \pipe\ thy protection \gresixstar\ up- \pipe\ on thy right hand.

The sun shall not \pipe\ burn thee by day: \gresixstar\ nor \pipe\ the moon by night.

The Lord keepeth thee \pipe\ from all evil: \gresixstar\ may the Lord \pipe\ keep \textbf{thy} soul.

May the Lord keep thy coming \pipe\ in \uline{and thy} go\uline{ing out}; \gresixstar\ from henceforth now \pipe\ and for ever.

Glory be to the \pipe\ Fa\uline{ther, and} to \uline{the Son}, \gresixstar\ and to the \pipe\ Holy Spirit.

As it was in the beginning, is now, and \pipe\ ever shall be, \gresixstar\ world without \pipe\ end. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2Ant5-02.tex}

}

\pend\pstart

% MONDAY CHAPTER

\subsection*{Chapter.\capitulumSpace \emph{2 Cor. 1, 3--4.}}

\pend\pstart

\begin{response}\lettrine{B}{l}essed be the God and Father of our Lord Jesus Christ, \gredagger\ the Father of mercies, and the God of all comfort, \gresixstar\ who comforteth us in all our tribulation. \Rbar\ Thanks be to God.

\end{response}

\pend\pstart

% MONDAY WINTER HYMN

\subsection*{Hymn.\\Winter Tone.}

\pend\pstart

\setspaceafterinitial{3mm plus 0em minus 0em}
\setspacebeforeinitial{3.8mm plus 0em minus 0em}

\myaboveinitial{VIII}
\includescore{EnglishVersion/F2/F2Hym-Hieme.tex}

\pend\pstart

\begin{response}
\Vbar\ O Lord, direct my prayer.\\
\Rbar\ As incense in thy sight.

\end{response}

\pend\pstart

% MONDAY SUMMER HYMN

\subsection*{Summer Tone.}

\pend\pstart

\setspaceafterinitial{2.2mm plus 0em minus 0em}
\setspacebeforeinitial{3.2mm plus 0em minus 0em}

\myaboveinitial{I}
\includescore{EnglishVersion/F2/F2Hym-Aestate.tex}

\pend\pstart

\begin{response}
\Vbar\ O Lord, direct my prayer.\\
\Rbar\ As incense in thy sight.

\end{response}

\pend\pstart

% MONDAY MAGNIFICAT

\subsection*{Canticle of the Blessed Virgin Mary.\capitulumSpace \emph{Luke 1, 46--55.}}

\pend\pstart

\setspaceafterinitial{3mm plus 0em minus 0em}
\setspacebeforeinitial{3.8mm plus 0em minus 0em}

\myaboveinitial{VIII G}
\includescore{EnglishVersion/F2/F2MagAnt-01.tex}
% My soul 

\pend\pstart

\begin{psalmtext}
Quia resp\'{e}xit humilit\'{a}tem anc\'{i}ll\ae\ \textbf{su}\ae\ : \gresixstar\ ecce enim ex hoc be\'{a}tam me dicent omnes gene\emph{rati}\textbf{\'{o}}nes.

Quia fecit mihi magna qui \textbf{po}tens e\libertineGlyph{s_t} : \gresixstar\ et san\libertineGlyph{c_t}um \emph{nomen} \textbf{e}jus.

Et miseric\'{o}rdia ejus a prog\'{e}nie in pro\textbf{g\'{e}}nies \gresixstar\ tim\'{e}n\emph{tibus} \textbf{e}um.

Fecit pot\'{e}ntiam in br\'{a}chio \textbf{su}o : \gresixstar\ disp\'{e}rsit sup\'{e}rbos mente \emph{cordis} \textbf{su}i.

Dep\'{o}suit pot\'{e}ntes de \textbf{se}de, \gresixstar\ et exal\emph{t\'{a}vit} \textbf{h\'{u}}miles.

Esuri\'{e}ntes impl\'{e}vit \textbf{bo}nis : \gresixstar\ et d\'{i}vites dim\'{i}\emph{sit i}\textbf{n\'{a}}nes.

Susc\'{e}pit Israel p\'{u}erum \textbf{su}um, \gresixstar\ record\'{a}tus miseric\'{o}r\emph{di\ae} \textbf{su}\ae.

Sicut loc\'{u}tus e\libertineGlyph{s_t} ad patres \textbf{nos}tros, \gresixstar\ Abraham, et s\'{e}mini e\emph{jus in} \textbf{s\'{\ae}}cula.

Glória Patri, et \textbf{Fí}lio, \gresixstar\ et Spirí\emph{tui} \textbf{Sanc}to.

Sicut erat in princípio, et nunc, et \textbf{sem}per, \gresixstar\ et in sǽcula sæcu\emph{lórum}. \textbf{A}men.

\end{psalmtext}

\pend\pstart

{\noinitial
\includescore{EnglishVersion/F2/F2MagAnt-02.tex}
% Ant. My soul * magnifies the Lord, because God has regarded my lowliness.
}

\pend\endnumbering
\end{Rightside}
\end{pages}
\Pages
